### 2013-03-12 doc/mandc2013/theory_paper/slattery_wilson_evans.tex
updates to mandc

The purpose of this study is to provide a simple, analytic theory
based on the properties of the linear system that will allow for
estimates of the domain decomposed behavior of the adjoint
Neumann-Ulam method. When solving problems where the linear operator
is symmetric, a host of analytic theories exist based on the
eigenvalue spectrum of the operator that characterize their behavior
in the context of deterministic linear solvers. Using past work, these
theories are adapted to the domain decomposed adjoint Neumann-Ulam
method using the one-speed, two-dimensional neutron diffusion
equation. In this paper we describe the adjoint Neumann-Ulam Monte
Carlo method followed by a presentation of the model problem. Using
the linear system generated by the discretization of this, we use a
spectral analysis to generate analytic relations for the eigenvalues
of the operator based on system parameters. Using the eigenvalue
spectra, we then build relationships to characterize the transport of
stochastic histories in a decomposed domain and the fraction of
histories that leak from a domain and will therefore have to be
communicated. Finally, we compare these analytic results to numerical
experiments conducted with the model problem and draw conclusions
looking towards future work.

>>>>

The purpose of this study is to provide a simple, analytic theory
based on the properties of the linear system that will allow for
estimates of the domain decomposed behavior of the adjoint
Neumann-Ulam method. When solving problems where the linear operator
is symmetric, a host of analytic theories exist based on the
eigenvalue spectrum of the operator that characterize their behavior
in the context of deterministic linear solvers. Using past work, these
theories are adapted to the domain decomposed adjoint Neumann-Ulam
method using the one-speed, two-dimensional neutron diffusion
equation. In this paper we describe the adjoint Neumann-Ulam Monte
Carlo method followed by a presentation of the model problem. Using
the linear system generated by the discretization of the model
problem, we use a spectral analysis to generate analytic relations for
the eigenvalues of the operator based on system parameters. Using the
eigenvalue spectra, we then build relationships to characterize the
transport of stochastic histories in a decomposed domain and the
fraction of histories that leak from a domain and will therefore have
to be communicated. Finally, we compare these analytic results to
numerical experiments conducted with the model problem and draw
conclusions looking towards future work.
